---
title: "project"
author: "Esraa"
date: "7/27/2019"
output: html_document
---

##Introduction

##Background

Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it. In this project, your goal will be to use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants. They were asked to perform barbell lifts correctly and incorrectly in 5 different ways. More information is available from the website here: http://web.archive.org/web/20161224072740/http:/groupware.les.inf.puc-rio.br/har (see the section on the Weight Lifting Exercise Dataset).

##Data

The training data for this project are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-training.csv

The test data are available here:

https://d396qusza40orc.cloudfront.net/predmachlearn/pml-testing.csv






## The need libraries for the project
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
set.seed(12345)
library(caret)
library(ggplot2) 
library(e1071)
 
```

##Read data from files and Clean it for the analysis

 here data is read and cleaned in order not to affect the result by removing the columns that contains Nulls
```{r cars}


# read the data from the file
testing1<-read.csv(file="D:/DataSienceCoursera/Course 9/project01/pml-testing.csv",na.strings = c("NA", "#DIV/0!", ""))
training1<-read.csv(file="D:/DataSienceCoursera/Course 9/project01/pml-training.csv",na.strings = c("NA", "#DIV/0!", ""))

# remove null columns
colname <- colnames(training1)[!colSums(is.na(training1)) > 0]
 

colname <- colname[8: length(colname)]
training2 <- training1[colname]

 
```

 

## Data partining to training and testing

divide the training data to 2 parts one for training with the algorithm and the other for the validation. 
training data set is 75% of thr data 
and the rest 25% of the data for the testing data set

```{r pressure1, echo=TRUE}

inTrain<- createDataPartition(y=training2$classe, p = 3/4)[[1]]
training <- training2[inTrain, ]
testing <- training2[-inTrain, ]


```


## Building models

we will try many models for prediting the data  and construct confusionMatrix 

##1.Model: regression tree 

```{r pressure2, echo=TRUE}
library(rpart)
 rpartFit <- train(classe ~ .,
                   data = training,
                   "rpart" )
 prediction <- predict(rpartFit, newData = testing)
confusionMatrix(testing$classe, prediction)
```


##2.Model:Random forest
```{r pressure3, echo=TRUE}
#it took very long time to run 

#fit2 <- train(classe ~ ., method="rf", data=training )
#val2 <- predict(fit2, testing)
#confusionMatrix(testing$classe, val2)
 

```


##3.Model: Liner Discriminant Analysis
```{r pressure4, echo=TRUE}
model_lda <- train(classe ~ ., data = training, method = "lda")
pred_lda <- predict(model_lda, testing)
confusionMatrix(testing$classe, pred_lda)
```


## Data Predicting: regression tree  is used

```{r pressure5, echo=TRUE}
pred <- predict(rpartFit, newdata=testing1)
pred
```
 
