---
title: "project"
author: "Esraa"
date: "7/27/2019"
output: html_document
---
## The need libraries for the project
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(knitr)
set.seed(12345)
library(caret)
library(ggplot2) 
library(e1071)
 
```

##Read data from files and Clean it for the analysis

 here data is read and cleaned in order not to affect the result by removing the columns that contains Nulls
```{r cars}



testing1<-read.csv(file="D:/DataSienceCoursera/Course 9/project01/pml-testing.csv",na.strings = c("NA", "#DIV/0!", ""))
training1<-read.csv(file="D:/DataSienceCoursera/Course 9/project01/pml-training.csv",na.strings = c("NA", "#DIV/0!", ""))

colname <- colnames(training1)[!colSums(is.na(training1)) > 0]
 

colname <- colname[8: length(colname)]
training2 <- training1[colname]


is.element(colname, colnames(testing1))


```

 

## Data partining to training and testing

divide the training data to 2 parts one for training with the algorithm and the other for the validation. 

```{r pressure1, echo=TRUE}

inTrain<- createDataPartition(y=training2$classe, p = 3/4)[[1]]
training <- training2[inTrain, ]
testing <- training2[-inTrain, ]


```


## Building models

we will try many models for prediting the data

##1.Model: regression tree 

```{r pressure2, echo=TRUE}


library(rpart)
 rpartFit <- train(classe ~ .,
                   data = training,
                   "rpart" )
 prediction <- predict(rpartFit, newData = testing)
 #confusionMatrix(testing$classe, prediction)
```


##2.Model:Random forest
```{r pressure3, echo=TRUE}
#it took very long time to run 

#fit2 <- train(classe ~ ., method="rf", data=training )
#val2 <- predict(fit2, testing)
#confusionMatrix(testing$classe, val2)
 

```


##3.Model: Liner Discriminant Analysis
```{r pressure4, echo=TRUE}
 model_lda <- train(classe ~ ., data = training, method = "lda")
 pred_lda <- predict(model_lda, testing)
 confusionMatrix(testing$classe, pred_lda)
 

```


## Data Predicting: regression tree  is used

```{r pressure5, echo=TRUE}

 pred <- predict(rpartFit, newdata=testing1)
pred

```
 
